\papertitle

### 2021-03-05 source_separation/paper/paper.tex
Add examples of source sounds

		\subsection{Data}
		We created our own targets as combinations of four sub-targets. The sub-targets come from the NIGENS \cite{NIGENS} and BBC \cite{BBC} databases, and freesound.org \cite{freesound}. We selected a total of 90 samples from these databases, choosing sounds that fit the following criteria:

		\begin{enumerate}
			\item Static sounds in which the harmonic average across time is a fitting representation of the sound
			\item Sounds in which there is at least some pitched content and not only noise
		\end{enumerate}			
		Each target that we used for testing was a combination of 4 randomly chosen source sounds from the group of 90 sounds. During the creation of the targets, the sources were randomly offset in time from the beginning of the target, so that they began playing at different times.

>>>>

		\subsection{Data}
		We created our own targets as combinations of four source sounds. The sources come from the NIGENS \cite{NIGENS} and BBC \cite{BBC} databases, and freesound.org \cite{freesound}. We selected a total of 90 samples from these databases, choosing sounds that fit the following criteria:

		\begin{enumerate}
			\item Static sounds in which the harmonic average across time is a fitting representation of the sound
			\item Sounds in which there is at least some pitched content and not only noise
		\end{enumerate}			
		The sounds chosen include alarms, bells, engine noises, animals, soundscapes, synthesizer chords, and sound effects. Each target that we used for testing was a combination of 4 randomly chosen source sounds from the group of 90 sounds. During the creation of the targets, the sources were randomly offset in time from the beginning of the target, so that they began playing at different times.
